Towards Detecting Stalkerware Through Network Traces

### 2019-03-22 paper/main.tex
Update main.tex
fixes to charts

\appendix

\section{Apps and Signatures}
\begin{table*}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	App & Signature & Relevant Info \\
	\midrule
	HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & Same as TheTruthSpy HTTP \\

@@

	Mobile Surveillance and Security
	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
	Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\

@@

\begin{table*}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	App & Signature & Relevant Info \\
	\midrule
	Norton Family parental control & \makecell{domain: spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
	User-Agent: NOF/4.9.2.12/Android/8.1.0\\
	SNI: family.norton.com} & HTTP POST with protobufs, or TLS. \\

@@

@@

\end{table*}
\end{document}

>>>>

\appendix
\clearpage
\begin{table*}

	\section{Apps and Signatures}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	App & Signature & Relevant Info \\
	\midrule
	HelloSpy & \makecell{HTTP Post to\\ <numbers>.dedicated.codero.net} & Same as TheTruthSpy HTTP \\

@@

@@

\begin{table*}
\begin{tabular}{p{5cm}p{5cm}p{5cm}}
	\toprule
	App & Signature & Relevant Info \\
	\midrule
		Mobile Surveillance and Security
	by Trackview & \makecell{HTTP req:\\ "GET /create\_session HTTP/1.1"\\ User agent:test \\Host:relay.google.com\\
		Domains: relay.l.google.com,\\ stun.l.google.com} & Uses STUN protocol \\

	Norton Family parental control & \makecell{domain: spoc-muw1.norton.com,\\spoc-mue1.norton.com\\
	User-Agent: NOF/4.9.2.12/Android/8.1.0\\
	SNI: family.norton.com} & HTTP POST with protobufs, or TLS. \\

@@

\end{table*}
\clearpage

@@

\end{document}
